The Impact of Interview Disruptions on Data Quality in Social Surveys

### 2024-12-02 paper/paper.qmd
update paper

## Overview
We employ the statistical programming language R [@citeR] to process, analyze, and visualize survey data that investigates how disruptions during interviews impact response quality. The dataset for this study is sourced from [European Social Survey](https://ess.sikt.no/en/datafile/0c3f5fda-4fe0-42f2-b4c8-4ef093c0508f/7?tab=0&elems=de8c08b6-e406-4c56-92ee-4272818cae96_1), which offers a rich collection of data on societal attitudes and behaviors across numerous European countries. The dataset includes multiple subsets tailored for different stages of analysis, allowing for a systematic examination of how various factors affect survey response quality. The primary dataset used for modeling comprises 9,743 rows and 25 variables, which capture essential details, including types of disruptions (such as partner, child, or other familial interference), methods of interview, and characteristics of respondents. The meticulous standardization of data collection across countries in the ESS ensures comparability and facilitates an in-depth exploration of the impacts of contextual disruptions on response quality.

>>>>

## Overview
We employ the statistical programming language R [@citeR] to process, analyze, and visualize survey data that investigates how disruptions during interviews impact response quality. The dataset for this study is sourced from [European Social Survey](https://ess.sikt.no/en/datafile/0c3f5fda-4fe0-42f2-b4c8-4ef093c0508f/7?tab=0&elems=de8c08b6-e406-4c56-92ee-4272818cae96_1)[@ess_datafile], which offers a rich collection of data on societal attitudes and behaviors across numerous European countries. The dataset includes multiple subsets tailored for different stages of analysis, allowing for a systematic examination of how various factors affect survey response quality. The primary dataset used for modeling comprises 9,743 rows and 25 variables, which capture essential details, including types of disruptions (such as partner, child, or other familial interference), methods of interview, and characteristics of respondents. The meticulous standardization of data collection across countries in the ESS ensures comparability and facilitates an in-depth exploration of the impacts of contextual disruptions on response quality.
